---
title: "bimm143_class13"
author: "Fangchao He"
date: "5/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Sample genotypes in the MXL 1000 Genome project data

Here we focus on the Mexican ancestry in Los Angeles, California (MXL) population

What proportion of the Mexican Ancestry in Los Angeles sample population (MXL) are homozygous for the asthma associated SNP (G|G)?

```{r}
# Read CSV from ENSEMBLE
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
head(mxl)

```

```{r}
table(mxl$Genotype..forward.strand.)
```

Proportion or percent of total for each genotype
```{r}
(table(mxl$Genotype..forward.strand.) / nrow(mxl)) * 100
```

# Quality Scores in FASTQ files

The fourth line of a FASTQ sequence format file encodes the quality score that tells us how good the sequence at a given position is (i.e. how likely it is to be correct based on the instrument)
```{r}
library(seqinr)
library(gtools)
asc(s2c("DDDDCDEDCDDDDBBDDDCC@")) - 33
#phred < asc

```

```{r}
t <- read.table("rs8067378_ENSG00000172057.6.txt")
head(t)
```

```{r}
summary(t)
```

```{r}
AA <- t[t$geno == "A/A", ]
AG <- t[t$geno == "A/G" || t$geno == "G/A", ]
GG <- t[t$geno == "G/G", ]
```

```{r}
#boxplot(AA$exp, AG$exp, GG$exp,)
boxplot(exp ~ geno, data = t)
```